Measuring Hash Trustworthiness via Collision Utility Metrics: Logical Cryptanalysis of MD4

### 2017-12-05 dsn-2018/bare_conf.tex
Expand New Collisions, add better figure
Signed-off-by: Alexander Scheel <alexander.m.scheel@gmail.com>

\textbf{TODO - figures and graphics on dataset, cross round, etc.}

>>>>

Further, compared to the work presented by M. Schl{\"a}ffer and E. Oswald in
\cite{Schlaffer2006}, this is a 35 fold increase. Increasing this bound is
possible with low additional cost. Further, by fully considering the
similarities of collision families under $\precsim$ and better enumerating the
resulting candidates, additional paths with unique differentials could be
constructed.
